Kaggle-in-class Data Challenges can Boost Student Learning

### 2018-04-20 paper-kaggle.Rmd
small change that was back ed out of

#summary(scores_5242$perf)
#summary(scores_2420$perf)
scores <- bind_rows(scores_5242, scores_2420)
ggplot(scores, aes(x=class, y=perf)) + 
  geom_boxplot() + 
  xlab("Participated in competiton") +
  ylab("RE")
```

>>>>

#summary(scores_5242$perf)
#summary(scores_2420$perf)
scores <- bind_rows(scores_5242, scores_2420)
ggplot(scores, aes(x=class, y=perf)) + 
  geom_boxplot() + 
  xlab("Participated in competition") +
  ylab("RE")
```
